---
title: "Demonstration page of R Markdown in combination with corporate theming"
author: "Flash Gordon, consultant economist"
date: "9 September 2017"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    self_contained: yes
    css: corp-styles.css
    highlight: pygments
---

<img src="logo.svg" style="position:absolute;top:0px;right:0px;" />
<div class="watermark">DRAFT</div>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE, eval = TRUE)
```

# Executive Summary

```{r results = 'asis'}
cat(stri_rand_lipsum(1))
```


# Purpose

This is basically just a demo of how to deal with a few issues with making R Markdown files comply with corporate styling - fonts, logo, heading sizes and colours, etc.  The [source code of the mini-project that builds this file is on GitHub](https://github.com/ellisp/rmarkdown-corporate-eg).  There is also an accompanying [blog post](http://ellisp.github.io/blog/2017/09/09/rmarkdown) on Peter's Stats Stuff.

The features include:

* logo in the top right of the document, and modify the title's width to allow for it
* heading styles and fonts in the html
* fonts and corporate colours used in the graphics
* document builds successfully even if the project is on a mapped network drive which usually causes problems with RStudio Server and Pandoc

# Analysis

## Data

We found this data from [MBIE's website](http://www.mbie.govt.nz/info-services/sectors-industries/tourism/tourism-research-data/monthly-regional-tourism-estimates/data-download).  MBIE is the Ministry of Business, Innovation and Employment.  This dataset represents estimated spend per month by tourists, broken down by product and country of origin.

## Findings

### Raw data

We see a very strong seasonal pattern, and also that people spend a lot on accommodation, food and beverage, and retail.

```{r}
p <- mrtes %>%
  # make products friendly with line wraps for the facet titles:
  mutate(Product = str_wrap(Product, 20)) %>%
  # add up all the "others""
  group_by(Date, Product, rto_lumped) %>%
  summarise(Spend = sum(Spend)) %>%
  ungroup() %>%
  mutate(rto_lumped = fct_reorder(rto_lumped, -Spend)) %>%
  ggplot(aes(x = Date, y = Spend, colour = rto_lumped)) +
  facet_wrap(~Product, scales = "free_y") +
  theme(legend.position = c(0.9, 0.1)) +
  labs(x = "", colour = "")

p + geom_line() + labs(y = "Spend ($m)")
```


### Seasonally adjusted

Some of the pattern is obscured by the strongly seasonal element.  There are more tourists in summer than winter in New Zealand.  We can use statistical methods to adjust for the seasonality and focus more on the trend.  NOte the big spike in food and beverage sales in Auckland in particular at the time of the 2011 Rugby World Cup.  Also not challenges with seasonal adjustment of accommodation spend in Auckland.  We could consider using more sophisticated methods to understand what is going on here.


```{r}
p +   stat_stl(frequency = 12, s.window = 7) +
  labs(y = "Seasonall adjusted spend ($m)")

```


### Food and Bev versus accommodation

We get some interesting patterns if we compare the percentage of total tourism spend on accommodation compared to food and beverage.  The sking location of Ruapehu stands out as having much more spend on accommodation and relatively little on food and beverage.  However, this may reflect the data collection process - if food and beverages are purchased from tourist's hotels, it will show up as accommodation:

```{r}
mrtes %>%
  group_by(rto_short, Product) %>%
  summarise(total_spend = sum(Spend)) %>%
  group_by(rto_short) %>%
  mutate(prop_spend = total_spend / sum(total_spend)) %>%
  filter(Product %in% c("Accommodation services", "Food and beverage serving services")) %>%
  select(-total_spend) %>%
  spread(Product, prop_spend) %>%
  ggplot(aes(x = `Accommodation services`, y = `Food and beverage serving services`,
                    label = rto_short)) +
  geom_text() +
  scale_x_continuous(label = percent) +
  scale_y_continuous(label = percent)

```
